Modelling the gas kinematics of an atypical Lyman alpha emitting compact dwarf galaxy

### 2017-03-19 paper/paper.tex
rename delete
bib in main text

This theoretical prediction was only confirmed thirty years later on
distant, relatively young, not primordial, galaxies \citep{1998ApJ...498L..93D}.
Currently Lyman Alpha Emitting (LAE) galaxies are commonly targeted
in surveys. 
The presence of the \lya\ emission line provides confirmation of
the distance of a galaxy while provides clues about the stellar
population and inter-stellar medium conditions regulating the
\lya\ emission.
A careful clustering analysis of LAEs can also yield clues about their link
to dark matter halos \cite{2016ApJ...828....5M}.

@@

\begin{table}
\begin{center}
\begin{tabular}{lc}\hline
$\alpha$(2000)$^{a}$ & 12h17min17.1s\\
$\delta$(2000)$^{b}$ & -28d02m32s\\
$l$, $b$ (deg) & 294, 34\\
$m_V$ & 17.5\\
  M$_V$ & -17.6\\ 
$v$(km s$^{-1}$) & 7795\\
\lya\ (erg cm$^{-2}$ s$^{-1}$ \AA$^{-1}$)& $8.1\times 10^{-14}$ \\
\lya\ Equivalent Width (\AA) & $70$\\
$21$cm (Jy km s$^{-1}$)& $<0.10$ \\\hline
\end{tabular}
\end{center}
\caption{Basic observational characteristics of TOL1214-277
  \citep{Thuan97}\label{obstable}} 
\end{table}

@@

\begin{figure*}
\begin{center}
  \includegraphics[width=0.6\textwidth]{vinf_cl.pdf}
  \includegraphics[width=0.6\textwidth]{P_cl.pdf}
  \includegraphics[width=0.6\textwidth]{sigma_cl.pdf}
\caption{Results from the multiphase
  model.
  The left column corresponds to the parameter's integrated distributions for
  models with the lowest $\chi^2$ values (dotted line) compared against the
  parameter's integrated distributions (continous line) used as a prior.
  These are the only three parameters that show a significant statistical difference from
  the prior distributions, for all the other eleven parameters we
  cannot find any significant difference.
  The right column shows a scatter plot of $\chi^2$ (rescaled by a $1000$)
  and its corresponding physical parameters.
  Only the  25 models with the lowest $\chi^2$ are included.
  \label{multiphaseresults}
}  
\end{center}
\end{figure*}

@@

We explore flat priors on four parameters: $200<V_{\rm
  max}/\mathrm{km\ s}^{-1} <600$,   $6.0<\log_{10}\tau<9.0$,
$4.0<\log_{10} T/10^4\mathrm{K}< 4.5$ and $0<\theta<90$ using $500$
steps with $24$ walkers for a total of $12000$ points in the chain.
Previous exploratory work shows that it is impossible to fit the
observed line outside thsese priors.
Finally, we estimate the parameter values from the 16th, 50th and 84th
percentiles.

@@

Why is it that the other parameters do not seem to matter? Probably
because $P_{cl}$ (the probability for a \lya\ to be emitted in a
clump) is high and most photons are produced at
large radii making the radiative tranfer effects in the center less
important.  
We cannot discard that another region of parameter spacem with similar
velocity structure but empty interclump medium, relatively dense
clumps and at least a few clumps per sightline 
could also work \citep{Hansen06}.
This possibility does not change our conclusions about the
kinematic parameters, but it might be interesting to explore in the
future with a higher sampling of the parameter space once new
observations clarify the kinematic nature of \tol.

@@

Using the constraints for the velocity dipersion $\sigma$ and the
maximum rotational velocity $V_m$ in a spherical system localized in a
region of size $r$ we can estimate two different values for the
dynamical mass within $r$:

@@

A new observational test is needed to clarify the kinematical nature of
\tol. 
We suggest that integral field unit measurements 
resolving its spatial extent are up to the task. 
\tol\ spans a region of $4$ arcseconds,
an instrument such as the Multi Unit Spectroscopic Explorer (MUSE)
\citep{2014Msngr.157...13B} with its
nominal $0.2$ arcseconds spatial sampling over a $1.0$ arcminute field
in wide-field mode could provide a coarse mapping of different
ionization lines to infer a kinematic map in the H$\alpha$ line,
following the kind of work presented by \citet{Herenz16} done with the Potsdam
Multi-Aperture Spectrometer (PMAS) \citet{PMAS} on nearby
\lya\ emitting galaxies.
We note that archival Chandra X-ray archival
data \footnote{\url{http://cxc.harvard.edu/cda/}} does not show any
detection for \tol.
This lack of detection would also put an upper limit on the intensity
of recent black hole activity due to accretion.

@@

\bibliographystyle{mn2e}
\bibliography{references}

>>>>

This theoretical prediction was only confirmed thirty years later on
distant, relatively young, not primordial, galaxies \citep{1998ApJ...498L..93D}.
Currently Lyman Alpha Emitting (LAE) galaxies are commonly targeted
in surveys. 
The presence of the \lya\ emission line provides confirmation of
the distance of a galaxy while provides clues about the stellar
population and inter-stellar medium conditions regulating the
\lya\ emission.
A careful clustering analysis of LAEs can also yield clues about their link
to dark matter halos \citep{2016ApJ...828....5M}.

@@

\begin{table}
\begin{center}
\begin{tabular}{lc}\hline
$\alpha$(2000)$^{a}$ & 12h17min17.1s\\
$\delta$(2000)$^{b}$ & -28d02m32s\\
$l$, $b$ (deg) & 294, 34\\
$m_V$ & 17.5\\
  M$_V$ & -17.6\\ 
$v$(km s$^{-1}$) & 7795\\
\lya\ (erg cm$^{-2}$ s$^{-1}$ \AA$^{-1}$)& $8.1\times 10^{-14}$ \\
\lya\ Equivalent Width (\AA) & $70$\\
$21$cm (Jy km s$^{-1}$)& $<0.10$ \\\hline
\end{tabular}
\end{center}
\caption{Basic observational characteristics of \tol\ 
  \citep{Thuan97}\label{obstable}} 
\end{table}

@@

\begin{figure*}
\begin{center}
  \includegraphics[width=0.6\textwidth]{vinf_cl.pdf}
  \includegraphics[width=0.6\textwidth]{P_cl.pdf}
  \includegraphics[width=0.6\textwidth]{sigma_cl.pdf}
\caption{Results from the multiphase
  model.
  The left column corresponds to the parameter's integrated distributions for
  models with the lowest $\chi^2$ values (dotted line) compared against the
  parameter's integrated distributions (continuous line) used as a prior.
  These are the only three parameters that show a significant statistical difference from
  the prior distributions, for all the other eleven parameters we
  cannot find any significant difference.
  The right column shows a scatter plot of $\chi^2$ (rescaled by a $1000$)
  and its corresponding physical parameters.
  Only the  25 models with the lowest $\chi^2$ are included.
  \label{multiphaseresults}
}  
\end{center}
\end{figure*}

@@

We explore flat priors on four parameters: $200<V_{\rm
  max}/\mathrm{km\ s}^{-1} <600$,   $6.0<\log_{10}\tau<9.0$,
$4.0<\log_{10} T/10^4\mathrm{K}< 4.5$ and $0<\theta<90$ using $500$
steps with $24$ walkers for a total of $12000$ points in the chain.
Previous exploratory work shows that it is impossible to fit the
observed line outside these priors.
Finally, we estimate the parameter values from the 16th, 50th and 84th
percentiles.

@@

Why is it that the other parameters do not seem to matter? Probably
because $P_{cl}$ (the probability for a \lya\ to be emitted in a
clump) is high and most photons are produced at
large radii making the radiative transfer effects in the center less
important.  
We cannot discard that another region of parameter space with similar
velocity structure but empty interclump medium, relatively dense
clumps and at least a few clumps per sightline 
could also work \citep{Hansen06}.
This possibility does not change our conclusions about the
kinematic parameters, but it might be interesting to explore in the
future with a higher sampling of the parameter space once new
observations clarify the kinematic nature of \tol.

@@

Using the constraints for the velocity dispersion $\sigma$ and the
maximum rotational velocity $V_m$ in a spherical system localized in a
region of size $r$ we can estimate two different values for the
dynamical mass within $r$:

@@

A new observational test is needed to clarify the kinematic nature of
\tol. 
We suggest that integral field unit measurements 
resolving its spatial extent are up to the task. 
\tol\ spans a region of $4$ arcseconds,
an instrument such as the Multi Unit Spectroscopic Explorer (MUSE)
\citep{2014Msngr.157...13B} with its
nominal $0.2$ arcseconds spatial sampling over a $1.0$ arcminute field
in wide-field mode could provide a coarse mapping of different
ionization lines to infer a kinematic map in the H$\alpha$ line,
following the kind of work presented by \citet{Herenz16} done with the Potsdam
Multi-Aperture Spectrometer (PMAS) \citet{PMAS} on nearby
\lya\ emitting galaxies.
We note that archival Chandra X-ray archival
data \footnote{\url{http://cxc.harvard.edu/cda/}} does not show any
detection for \tol.
This lack of detection would also put an upper limit on the intensity
of recent black hole activity due to accretion.

@@

\bibliographystyle{mn2e}
%\bibliography{references}
\begin{thebibliography}{}

\bibitem[\protect\citeauthoryear{{Bacon} et~al.,}{{Bacon}
  et~al.}{2014}]{2014Msngr.157...13B}
{Bacon} R.  et~al., 2014, The Messenger, 157, 13

\bibitem[\protect\citeauthoryear{{Dey}, {Spinrad}, {Stern}, {Graham} \&
  {Chaffee}}{{Dey} et~al.}{1998}]{1998ApJ...498L..93D}
{Dey} A.,  {Spinrad} H.,  {Stern} D.,  {Graham} J.~R.,    {Chaffee} F.~H.,
  1998, \apjl, 498, L93

\bibitem[\protect\citeauthoryear{{Dijkstra}}{{Dijkstra}}{2014}]{2014PASA...31...40D}
{Dijkstra} M.,  2014, \pasa, 31, e040

\bibitem[\protect\citeauthoryear{{Dijkstra}, {Lidz} \& {Wyithe}}{{Dijkstra}
  et~al.}{2007}]{2007MNRAS.377.1175D}
{Dijkstra} M.,  {Lidz} A.,    {Wyithe} J.~S.~B.,  2007, \mnras, 377, 1175

\bibitem[\protect\citeauthoryear{{Engelbracht}, {Rieke}, {Gordon}, {Smith},
  {Werner}, {Moustakas}, {Willmer} \& {Vanzi}}{{Engelbracht}
  et~al.}{2008}]{2008ApJ...678..804E}
{Engelbracht} C.~W.,  {Rieke} G.~H.,  {Gordon} K.~D.,  {Smith} J.-D.~T.,
  {Werner} M.~W.,  {Moustakas} J.,  {Willmer} C.~N.~A.,    {Vanzi} L.,  2008,
  \apj, 678, 804

\bibitem[\protect\citeauthoryear{{Erb} et~al.,}{{Erb} et~al.}{2014}]{Erb14}
{Erb} D.~K.  et~al., 2014, \apj, 795, 33

\bibitem[\protect\citeauthoryear{{Eskew}, {Zaritsky} \& {Meidt}}{{Eskew}
  et~al.}{2012}]{2012AJ....143..139E}
{Eskew} M.,  {Zaritsky} D.,    {Meidt} S.,  2012, \aj, 143, 139

\bibitem[\protect\citeauthoryear{{Foreman-Mackey}, {Hogg}, {Lang} \&
  {Goodman}}{{Foreman-Mackey} et~al.}{2013}]{2013PASP..125..306F}
{Foreman-Mackey} D.,  {Hogg} D.~W.,  {Lang} D.,    {Goodman} J.,  2013, \pasp,
  125, 306

\bibitem[\protect\citeauthoryear{{Forero-Romero}, {Yepes}, {Gottl{\"o}ber},
  {Knollmann}, {Cuesta} \& {Prada}}{{Forero-Romero} et~al.}{2011}]{CLARA}
{Forero-Romero} J.~E.,  {Yepes} G.,  {Gottl{\"o}ber} S.,  {Knollmann} S.~R.,
  {Cuesta} A.~J.,    {Prada} F.,  2011, \mnras, 415, 3666

\bibitem[\protect\citeauthoryear{{Garavito-Camargo}, {Forero-Romero} \&
  {Dijkstra}}{{Garavito-Camargo} et~al.}{2014}]{GaravitoCamargo2014}
{Garavito-Camargo} J.~N.,  {Forero-Romero} J.~E.,    {Dijkstra} M.,  2014,
  \apj, 795, 120

\bibitem[\protect\citeauthoryear{Goodman \& Weare}{Goodman \&
  Weare}{2010}]{goodman2010ensemble}
Goodman J.,  Weare J.,  2010, Communications in applied mathematics and
  computational science, 5, 65

\bibitem[\protect\citeauthoryear{{Gronke}, {Bull} \& {Dijkstra}}{{Gronke}
  et~al.}{2015}]{2015ApJ...812..123G}
{Gronke} M.,  {Bull} P.,    {Dijkstra} M.,  2015, \apj, 812, 123

\bibitem[\protect\citeauthoryear{{Gronke} \& {Dijkstra}}{{Gronke} \&
  {Dijkstra}}{2016}]{Gronke2016}
{Gronke} M.,  {Dijkstra} M.,  2016, \apj, 826, 14

\bibitem[\protect\citeauthoryear{{Hansen} \& {Oh}}{{Hansen} \&
  {Oh}}{2006}]{Hansen06}
{Hansen} M.,  {Oh} S.~P.,  2006, \mnras, 367, 979

\bibitem[\protect\citeauthoryear{{Harrington}}{{Harrington}}{1973}]{Harrington73}
{Harrington} J.~P.,  1973, \mnras, 162, 43

\bibitem[\protect\citeauthoryear{{Hayes}}{{Hayes}}{2015}]{Hayes15}
{Hayes} M.,  2015, \pasa, 32, e027

\bibitem[\protect\citeauthoryear{{Herenz} et~al.,}{{Herenz}
  et~al.}{2016}]{Herenz16}
{Herenz} E.~C.  et~al., 2016, \aap, 587, A78

\bibitem[\protect\citeauthoryear{{Hummer} \& {Storey}}{{Hummer} \&
  {Storey}}{1987}]{Hummer1987}
{Hummer} D.~G.,  {Storey} P.~J.,  1987, \mnras, 224, 801

\bibitem[\protect\citeauthoryear{{Izotov}, {Papaderos}, {Guseva}, {Fricke} \&
  {Thuan}}{{Izotov} et~al.}{2004}]{Izotov04}
{Izotov} Y.~I.,  {Papaderos} P.,  {Guseva} N.~G.,  {Fricke} K.~J.,    {Thuan}
  T.~X.,  2004, \aap, 421, 539

\bibitem[\protect\citeauthoryear{{Kennicutt}
  Jr.}{{Kennicutt}}{1998}]{Kennicutt98}
{Kennicutt} Jr. R.~C.,  1998, \araa, 36, 189

\bibitem[\protect\citeauthoryear{{Laursen}, {Duval} \& {{\"O}stlin}}{{Laursen}
  et~al.}{2013}]{Laursen2013ApJ...766..124L}
{Laursen} P.,  {Duval} F.,    {{\"O}stlin} G.,  2013, \apj, 766, 124

\bibitem[\protect\citeauthoryear{{Loeb} \& {Rybicki}}{{Loeb} \&
  {Rybicki}}{1999}]{LoebRybicki}
{Loeb} A.,  {Rybicki} G.~B.,  1999, \apj, 524, 527

\bibitem[\protect\citeauthoryear{{Madden} et~al.,}{{Madden}
  et~al.}{2014}]{2014PASP..126.1079M}
{Madden} S.~C.  et~al., 2014, \pasp, 126, 1079

\bibitem[\protect\citeauthoryear{{Mas-Hesse}, {Kunth}, {Tenorio-Tagle},
  {Leitherer}, {Terlevich} \& {Terlevich}}{{Mas-Hesse}
  et~al.}{2003}]{mashesse03}
{Mas-Hesse} J.~M.,  {Kunth} D.,  {Tenorio-Tagle} G.,  {Leitherer} C.,
  {Terlevich} R.~J.,    {Terlevich} E.,  2003, \apj, 598, 858

\bibitem[\protect\citeauthoryear{{Mej{\'{\i}}a-Restrepo} \&
  {Forero-Romero}}{{Mej{\'{\i}}a-Restrepo} \&
  {Forero-Romero}}{2016}]{2016ApJ...828....5M}
{Mej{\'{\i}}a-Restrepo} J.~E.,  {Forero-Romero} J.~E.,  2016, \apj, 828, 5

\bibitem[\protect\citeauthoryear{{Neufeld}}{{Neufeld}}{1991}]{1991ApJ...370L..85N}
{Neufeld} D.~A.,  1991, \apjl, 370, L85

\bibitem[\protect\citeauthoryear{{Noeske}, {Papaderos}, {Cair{\'o}s} \&
  {Fricke}}{{Noeske} et~al.}{2003}]{2003A&A...410..481N}
{Noeske} K.~G.,  {Papaderos} P.,  {Cair{\'o}s} L.~M.,    {Fricke} K.~J.,  2003,
  \aap, 410, 481

\bibitem[\protect\citeauthoryear{{{\"O}stlin} et~al.,}{{{\"O}stlin}
  et~al.}{2014}]{LARS}
{{\"O}stlin} G.  et~al., 2014, \apj, 797, 11

\bibitem[\protect\citeauthoryear{{Partridge} \& {Peebles}}{{Partridge} \&
  {Peebles}}{1967}]{PartridgePeebles}
{Partridge} R.~B.,  {Peebles} P.~J.~E.,  1967, \apj, 147, 868

\bibitem[\protect\citeauthoryear{{Prada}, {Klypin}, {Cuesta}, {Betancort-Rijo}
  \& {Primack}}{{Prada} et~al.}{2012}]{2012MNRAS.423.3018P}
{Prada} F.,  {Klypin} A.~A.,  {Cuesta} A.~J.,  {Betancort-Rijo} J.~E.,
  {Primack} J.,  2012, \mnras, 423, 3018

\bibitem[\protect\citeauthoryear{{Pustilnik} \& {Martin}}{{Pustilnik} \&
  {Martin}}{2007}]{pustilnikmartin07}
{Pustilnik} S.~A.,  {Martin} J.-M.,  2007, \aap, 464, 859

\bibitem[\protect\citeauthoryear{{Rivera-Thorsen} et~al.,}{{Rivera-Thorsen}
  et~al.}{2015}]{2015ApJ...805...14R}
{Rivera-Thorsen} T.~E.  et~al., 2015, \apj, 805, 14

\bibitem[\protect\citeauthoryear{{Roth} et~al.,}{{Roth} et~al.}{2005}]{PMAS}
{Roth} M.~M.  et~al., 2005, \pasp, 117, 620

\bibitem[\protect\citeauthoryear{{Seth} et~al.,}{{Seth}
  et~al.}{2014}]{2014Natur.513..398S}
{Seth} A.~C.  et~al., 2014, \nat, 513, 398

\bibitem[\protect\citeauthoryear{{Tasitsiomi}}{{Tasitsiomi}}{2006}]{2006ApJ...645..792T}
{Tasitsiomi} A.,  2006, \apj, 645, 792

\bibitem[\protect\citeauthoryear{{Thuan} \& {Izotov}}{{Thuan} \&
  {Izotov}}{1997}]{Thuan97}
{Thuan} T.~X.,  {Izotov} Y.~I.,  1997, \apj, 489, 623

\bibitem[\protect\citeauthoryear{{Tollerud}, {Bullock}, {Graves} \&
  {Wolf}}{{Tollerud} et~al.}{2011}]{2011ApJ...726..108T}
{Tollerud} E.~J.,  {Bullock} J.~S.,  {Graves} G.~J.,    {Wolf} J.,  2011, \apj,
  726, 108

\bibitem[\protect\citeauthoryear{{Trainor}, {Strom}, {Steidel} \&
  {Rudie}}{{Trainor} et~al.}{2016}]{Trainor16}
{Trainor} R.~F.,  {Strom} A.~L.,  {Steidel} C.~C.,    {Rudie} G.~C.,  2016,
  \apj, 832, 171

\bibitem[\protect\citeauthoryear{{Verhamme}, {Orlitov{\'a}}, {Schaerer} \&
  {Hayes}}{{Verhamme} et~al.}{2015}]{2015A&A...578A...7V}
{Verhamme} A.,  {Orlitov{\'a}} I.,  {Schaerer} D.,    {Hayes} M.,  2015, \aap,
  578, A7

\end{thebibliography}
